Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2024-05-10 code/L2/L2_1_TropicalAndes_taxdiv.Rmd
update input file for plant occ, create function for richness plots to reduce redundant code

# Read in Data
```{r}
TropicalAndes_plant_occ_forest <- read.csv(file.path(data_path_L1,"TropicalAndes_GBIF_plant_occ_cleaned.csv"))
TropicalAndes_frugivore_occ_forest <- read.csv(file.path(data_path_L1,"TropicalAndes_GBIF_frugivore_occ_cleaned_subset.csv"))
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path_L0, "Forest_sf.shp"), layer = "Forest_sf")
```

@@

# Plot TD/Richness

## 5 km resolution
### Make Grid
```{r}
#check units
st_crs(TApoly, parameters = TRUE)$units_gdal
st_crs(TApoly)
st_crs(TropicalAndes_IUCNHabitat_Forest)
```

```{r}
TAGrid_5 <- TApoly %>%
  st_make_grid(cellsize = c(5000)) %>%
  st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
  st_cast("MULTIPOLYGON") %>%
  st_sf() %>%
  mutate(cellid = row_number())
```

### Plot Empty Grid
```{r}
gridPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest) +
  geom_sf(data = TAGrid_5) +
  labs(title = "Tropical Andes Grid [5 km]", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

gridPlot
```

### Cell Richness
```{r}
plant_richness_grid_5 <- TAGrid_5 %>%
  st_join(plants_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

```{r}
frugivore_richness_grid_5 <- TAGrid_5 %>%
  st_join(frugivores_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

### Richness plots
```{r}
plantgridRichTA_5km <-
ggplot(plant_richness_grid_5) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Plant Richness [5 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

plantgridRichTA_5km
```

```{r}
frugivoregridRichTA_5km <-
ggplot(frugivore_richness_grid_5) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Frugivore Richness [5 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

frugivoregridRichTA_5km
```

## Extract cell values
```{r}
plant_cellRichness_5km <- plantgridRichTA_5km[["data"]]
frugivore_cellRichness_5km <- frugivoregridRichTA_5km[["data"]]
```

### Plant vs frugivore richness plot
```{r}
compare_richness_summary_5km <- summary(lm(frugivore_cellRichness_5km$num_species ~ plant_cellRichness_5km$num_species))
compare_richness_summary_5km

# save r-squared value
compare_richness_r2_5km <- compare_richness_summary_5km$r.squared
```

```{r}
plot(plant_cellRichness_5km$num_species, frugivore_cellRichness_5km$num_species,
     main = "Plant Richness vs Frugivore Richness [5 km]",
     xlab = "Plant Richness by cell", ylab = "Frugivore Richness by cell")
abline(lm(frugivore_cellRichness_5km$num_species ~ plant_cellRichness_5km$num_species))
```

```{r}
hist(plant_cellRichness_5km$num_species,
     main = "Histogram of Plant Richness by cell",
     xlab = "Plant Richness by cell")
hist(frugivore_cellRichness_5km$num_species,
     main = "Histogram of Frugivore Richness by cell",
     xlab = "Frugivore Richness by cell")
```

## 25 km 
### Make Grid
```{r}
TAGrid_25 <- TApoly %>%
  st_make_grid(cellsize = c(25000)) %>%
  st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
  st_cast("MULTIPOLYGON") %>%
  st_sf() %>%
  mutate(cellid = row_number())
```

### Plot Empty Grid
```{r}
gridPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest) +
  geom_sf(data = TAGrid_25) +
  labs(title = "Tropical Andes Grid [25 km]", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

gridPlot
```

### Cell Richness
```{r}
plant_richness_grid_25 <- TAGrid_25 %>%
  st_join(plants_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

```{r}
frugivore_richness_grid_25 <- TAGrid_25 %>%
  st_join(frugivores_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

### Richness plots
```{r}
plantgridRichTA_25km <-
ggplot(plant_richness_grid_25) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Plant Richness [25 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

plantgridRichTA_25km
```

```{r}
frugivoregridRichTA_25km <-
ggplot(frugivore_richness_grid_25) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Frugivore Richness [25 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

frugivoregridRichTA_25km
```

## Extract cell values
```{r}
plant_cellRichness_25km <- plantgridRichTA_25km[["data"]]
frugivore_cellRichness_25km <- frugivoregridRichTA_25km[["data"]]
```

### Plant vs frugivore richness plot
```{r}
compare_richness_summary_25km <- summary(lm(frugivore_cellRichness_25km$num_species ~ plant_cellRichness_25km$num_species))
compare_richness_summary_25km

# save r-squared value
compare_richness_r2_25km <- compare_richness_summary_25km$r.squared
```

```{r}
plot(plant_cellRichness_25km$num_species, frugivore_cellRichness_25km$num_species,
     main = "Plant Richness vs Frugivore Richness [25 km]",
     xlab = "Plant Richness by cell", ylab = "Frugivore Richness by cell")
abline(lm(frugivore_cellRichness_25km$num_species ~ plant_cellRichness_25km$num_species))
```

```{r}
hist(plant_cellRichness_25km$num_species,
     main = "Histogram of Plant Richness by cell",
     xlab = "Plant Richness by cell")
hist(frugivore_cellRichness_25km$num_species,
     main = "Histogram of Frugivore Richness by cell",
     xlab = "Frugivore Richness by cell")
```

## 50 km 
### Make Grid
```{r}
TAGrid_50 <- TApoly %>%
  st_make_grid(cellsize = c(50000)) %>%
  st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
  st_cast("MULTIPOLYGON") %>%
  st_sf() %>%
  mutate(cellid = row_number())
```

### Plot Empty Grid
```{r}
gridPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest) +
  geom_sf(data = TAGrid_50) +
  labs(title = "Tropical Andes Grid [50 km]", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

gridPlot
```

### Cell Richness
```{r}
plant_richness_grid_50 <- TAGrid_50 %>%
  st_join(plants_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

```{r}
frugivore_richness_grid_50 <- TAGrid_50 %>%
  st_join(frugivores_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

### Richness plots
```{r}
plantgridRichTA_50km <-
ggplot(plant_richness_grid_50) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Plant Richness [50 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

plantgridRichTA_50km
```

```{r}
frugivoregridRichTA_50km <-
ggplot(frugivore_richness_grid_50) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Frugivore Richness [50 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

frugivoregridRichTA_50km
```

## Extract cell values
```{r}
plant_cellRichness_50km <- plantgridRichTA_50km[["data"]]
frugivore_cellRichness_50km <- frugivoregridRichTA_50km[["data"]]
```

### Plant vs frugivore richness plot
```{r}
compare_richness_summary_50km <- summary(lm(frugivore_cellRichness_50km$num_species ~ plant_cellRichness_50km$num_species))
compare_richness_summary_50km

# save r-squared value
compare_richness_r2_50km <- compare_richness_summary_50km$r.squared
```

```{r}
plot(plant_cellRichness_50km$num_species, frugivore_cellRichness_50km$num_species,
     main = "Plant Richness vs Frugivore Richness [50 km]",
     xlab = "Plant Richness by cell", ylab = "Frugivore Richness by cell")
abline(lm(frugivore_cellRichness_50km$num_species ~ plant_cellRichness_50km$num_species))
```

```{r}
hist(plant_cellRichness_50km$num_species,
     main = "Histogram of Plant Richness by cell",
     xlab = "Plant Richness by cell")
hist(frugivore_cellRichness_50km$num_species,
     main = "Histogram of Frugivore Richness by cell",
     xlab = "Frugivore Richness by cell")
```

## 75 km 
### Make Grid
```{r}
TAGrid_75 <- TApoly %>%
  st_make_grid(cellsize = c(75000)) %>%
  st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
  st_cast("MULTIPOLYGON") %>%
  st_sf() %>%
  mutate(cellid = row_number())
```

### Plot Empty Grid
```{r}
gridPlot <-
ggplot() +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TropicalAndes_IUCNHabitat_Forest) +
  geom_sf(data = TAGrid_75) +
  labs(title = "Tropical Andes Grid [75 km]", x = "Latitude", y = "Longitude") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

gridPlot
```

### Cell Richness
```{r}
plant_richness_grid_75 <- TAGrid_75 %>%
  st_join(plants_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

```{r}
frugivore_richness_grid_75 <- TAGrid_75 %>%
  st_join(frugivores_sf_species) %>%
  mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
  group_by(cellid) %>%
  summarize(num_species = sum(overlap))
```

### Richness plots
```{r}
plantgridRichTA_75km <-
ggplot(plant_richness_grid_75) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Plant Richness [75 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
  coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

plantgridRichTA_75km
```

```{r}
frugivoregridRichTA_75km <-
ggplot(frugivore_richness_grid_75) +
  geom_sf(data = Americas, fill = "white") +
  geom_sf(data = TApoly, fill = "grey", size = 0.1) +
  geom_sf(aes(fill = num_species), color = NA) +
  scale_fill_scico(palette = "romaO", direction = 1) +
  labs(title = "Tropical Andes Frugivore Richness [75 km]", x = "Longitude", y = "Latitude",
       fill = "Number of species") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
    pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
  theme(panel.background = element_rect(fill = "lightblue"))

frugivoregridRichTA_75km
```

## Extract cell values
```{r}
plant_cellRichness_75km <- plantgridRichTA_75km[["data"]]
frugivore_cellRichness_75km <- frugivoregridRichTA_75km[["data"]]
```

### Plant vs frugivore richness plot
```{r}
compare_richness_summary_75km <- summary(lm(frugivore_cellRichness_75km$num_species ~ plant_cellRichness_75km$num_species))
compare_richness_summary_75km

# save r-squared value
compare_richness_r2_75km <- compare_richness_summary_75km$r.squared
```

# Compare r-squared by resolution
Plot
# Multi panel plots
Richness maps
# Write data to csv
```{r}
write.csv(plant_cellRichness0.75, file.path(output_path,"TropicalAndes_GBIF_plant_richness_sub.csv"))
write.csv(frugivore_cellRichness0.75, file.path(output_path,"TropicalAndes_frugivore_richness_sub.csv"))
```

>>>>

# Read in Data
```{r}
TropicalAndes_plant_occ_forest <- read.csv(file.path(data_path_L1,"TropicalAndes_GBIF_plant_occ_cleaned_subset.csv"))
TropicalAndes_frugivore_occ_forest <- read.csv(file.path(data_path_L1,"TropicalAndes_GBIF_frugivore_occ_cleaned_subset.csv"))
TropicalAndes_IUCNHabitat_Forest <- read_sf(file.path(data_path_L0, "Forest_sf.shp"), layer = "Forest_sf")
```

@@

```{r}
#check units
st_crs(TApoly, parameters = TRUE)$units_gdal
st_crs(TApoly)
st_crs(TropicalAndes_IUCNHabitat_Forest)
```

# Plot TD/Richness
function for richness plots
```{r}
create_rich_plots <- function(resolution_meters) {
  # Make Grid
  TAGrid <- TApoly %>%
    st_make_grid(cellsize = c(resolution_meters)) %>%
    st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
    st_cast("MULTIPOLYGON") %>%
    st_sf() %>%
    mutate(cellid = row_number())

  # Plot Empty Grid
  gridPlot <- ggplot() +
    geom_sf(data = Americas, fill = "white") +
    geom_sf(data = TropicalAndes_IUCNHabitat_Forest) +
    geom_sf(data = TAGrid) +
    labs(title = paste("Tropical Andes Grid [", resolution_meters/1000, " km]", sep=""), x = "Latitude", y = "Longitude") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    annotation_scale(location = "bl", width_hint = 0.5) +
    annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.3, "in"), 
                           pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
    theme(panel.background = element_rect(fill = "lightblue"))

  print(gridPlot)

  # Calculate cell richness for plants
  plant_richness_grid <- TAGrid %>%
    st_join(plants_sf_species) %>%
    mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
    group_by(cellid) %>%
    summarize(num_species = sum(overlap))

  # Calculate cell richness for frugivores
  frugivore_richness_grid <- TAGrid %>%
    st_join(frugivores_sf_species) %>%
    mutate(overlap = ifelse(!is.na(species), 1, 0)) %>%
    group_by(cellid) %>%
    summarize(num_species = sum(overlap))

  # Plot richness for plants
  plantgridRichTA <- ggplot(plant_richness_grid) +
    geom_sf(data = Americas, fill = "white") +
    geom_sf(data = TApoly, fill = "grey", size = 0.1) +
    geom_sf(aes(fill = num_species), color = NA) +
    scale_fill_scico(palette = "romaO", direction = 1) +
    labs(title = paste("Tropical Andes Plant Richness [", resolution_meters/1000, " km]", sep=""), x = "Longitude", y = "Latitude",
         fill = "Number of species") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    annotation_scale(location = "bl", width_hint = 0.5) +
    annotation_north_arrow(location = "bl", which_north = "true", 
                           pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
    theme(panel.background = element_rect(fill = "lightblue"))

  print(plantgridRichTA)

  # Plot richness for frugivores
  frugivoregridRichTA <- ggplot(frugivore_richness_grid) +
    geom_sf(data = Americas, fill = "white") +
    geom_sf(data = TApoly, fill = "grey", size = 0.1) +
    geom_sf(aes(fill = num_species), color = NA) +
    scale_fill_scico(palette = "romaO", direction = 1) +
    labs(title = paste("Tropical Andes Frugivore Richness [", resolution_meters/1000, " km]", sep=""), x = "Longitude", y = "Latitude",
         fill = "Number of species") +
    coord_sf(xlim = c(-85, -54), ylim = c(-24, 14), expand = FALSE, crs = 4326) +
    annotation_scale(location = "bl", width_hint = 0.5) +
    annotation_north_arrow(location = "bl", which_north = "true", 
                           pad_x = unit(0.3, "in"), pad_y = unit(0.3, "in"), style = north_arrow_fancy_orienteering) +
    theme(panel.background = element_rect(fill = "lightblue"))

  print(frugivoregridRichTA)

  # Extract cell values
  plant_cellRichness <- plantgridRichTA[["data"]]
  frugivore_cellRichness <- frugivoregridRichTA[["data"]]

  ### Plant vs frugivore richness plot
  compare_richness_summary <- summary(lm(frugivore_cellRichness$num_species ~ plant_cellRichness$num_species))
  print(compare_richness_summary)

  # save r-squared value
  compare_richness_r2 <- compare_richness_summary$r.squared

  plant_frug_richness_compare <- plot(plant_cellRichness$num_species, frugivore_cellRichness$num_species,
       main = paste("Plant Richness vs Frugivore Richness [", resolution_meters/1000, " km]", sep = ""),
       xlab = "Plant Richness by cell", ylab = "Frugivore Richness by cell")
  abline(lm(frugivore_cellRichness$num_species ~ plant_cellRichness$num_species))

  print(plant_frug_richness_compare)

  plant_richness_hist <- hist(plant_cellRichness$num_species,
       main = paste("Histogram of Plant Richness [", resolution_meters/1000, " km] by cell", sep = ""),
       xlab = "Plant Richness by cell")
  print(plant_richness_hist)
  frugivore_richness_hist <- hist(frugivore_cellRichness$num_species,
       main = paste("Histogram of Frugivore Richness [", resolution_meters/1000, " km] by cell", sep = ""),
       xlab = "Frugivore Richness by cell")
  print(frugivore_richness_hist)
}

```

## 1 km resolution
```{r}
richness_1km <- create_rich_plots(1000)
# save plots
plantgridRichTA_1km <- plantgridRichTA
frugivoregridRichTA_1km <- frugivoregridRichTA
# save richness data
plant_cellRichness_1km <- plant_cellRichness
frugivore_cellRichness_1km <- frugivore_cellRichness

compare_richness_r2_1km <- compare_richness_r2
```

## 5 km resolution
```{r}
richness_5km <- create_rich_plots(5000)
# save plots
plantgridRichTA_5km <- plantgridRichTA
frugivoregridRichTA_5km <- frugivoregridRichTA
## Extract cell values
plant_cellRichness_5km <- plant_cellRichness
frugivore_cellRichness_5km <- frugivore_cellRichness

compare_richness_r2_5km <- compare_richness_r2
```

## 10 km
```{r}
richness_10km <- create_rich_plots(10000)
# save plots
plantgridRichTA_10km <- plantgridRichTA
frugivoregridRichTA_10km <- frugivoregridRichTA
## Extract cell values
plant_cellRichness_10km <- plant_cellRichness
frugivore_cellRichness_10km <- frugivore_cellRichness

compare_richness_r2_10km <- compare_richness_r2
```

## 25 km
```{r}
richness_25km <- create_rich_plots(25000)
# save plots
plantgridRichTA_25km <- plantgridRichTA
frugivoregridRichTA_25km <- frugivoregridRichTA
## Extract cell values
plant_cellRichness_25km <- plant_cellRichness
frugivore_cellRichness_25km <- frugivore_cellRichness

compare_richness_r2_25km <- compare_richness_r2
```

## 50 km
```{r}
richness_50km <- create_rich_plots(50000)
# save plots
plantgridRichTA_50km <- plantgridRichTA
frugivoregridRichTA_50km <- frugivoregridRichTA
## Extract cell values
plant_cellRichness_50km <- plant_cellRichness
frugivore_cellRichness_50km <- frugivore_cellRichness

compare_richness_r2_50km <- compare_richness_r2
```

## 75 km 
```{r}
richness_75km <- create_rich_plots(75000)
# save plots
plantgridRichTA_75km <- plantgridRichTA
frugivoregridRichTA_75km <- frugivoregridRichTA
## Extract cell values
plant_cellRichness_75km <- plant_cellRichness
frugivore_cellRichness_75km <- frugivore_cellRichness

compare_richness_r2_75km <- compare_richness_r2
```

## 100 km 
```{r}
richness_100km <- create_rich_plots(100000)
# save plots
plantgridRichTA_100km <- plantgridRichTA
frugivoregridRichTA_100km <- frugivoregridRichTA
## Extract cell values
plant_cellRichness_100km <- plant_cellRichness
frugivore_cellRichness_100km <- frugivore_cellRichness

compare_richness_r2_100km <- compare_richness_r2
```

# Compare r-squared by resolution
Plot
```{r}
# create dataframe of resolutions and r-squared values
resolution <- c("5", "25", "50", "75", "100")
r_squared <- c(compare_richness_r2_5km, compare_richness_r2_25km, compare_richness_r2_50km, compare_richness_r2_75km, compare_richness_r2_100km)
r_squared_compare <- data.frame(resolution, r-squared)
```

```{r}
ggplot(r_squared_compare, aes(x=resolution, y=r_squared)) +
  geom_point()+
  labs(title = "R-squared values of plant-frugivore richness relationships by resolution", x = "Resolution (km)", y = "R-squared",
       fill = "Number of species") 
```

# Multi panel plots
Richness maps
```{r}
grid.arrange(plot_1, plot_2, nrow = 1)
```

# Write data to csv
```{r}
write.csv(plant_cellRichness0.75, file.path(output_path,"TropicalAndes_GBIF_plant_richness_sub.csv"))
write.csv(frugivore_cellRichness0.75, file.path(output_path,"TropicalAndes_frugivore_richness_sub.csv"))
```
